Software Citation Principles

### 2016-02-23 sc-principles/software-citation-principles.tex
adding a bit more to the intro

The Force11 Software Citation Working Group~\cite{f11scwg} has been studying this,
beginning in ...  with a number of meetings ... and has prepared this document for
presentation at Force2016~\cite{force2016} and further discussion.  We expect that
this discussion may lead to a second, final version of this document, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.

>>>>

The Force11 Software Citation Working Group~\cite{f11scwg} was created in April 2015.
It gathered members, and then in June 2015 began studying this, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and draft this resulting document.
This document will be presented and discussed at the Force2016 Conference \cite{force2016}
in April 2016.  We expect that
this discussion may lead to a second, final version of this document, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.
